Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-11-14 limits/ms.tex
New sigp plots with real sigp, not sigpbar.

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.}
\label{2d mass reconstruction}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sb.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
\caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $B=0$ (green) and $B=0$ (blue). In both plots, the actual projected
  velocity dispersion of the mock data (black).
  }
\label{fig:sigp}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ {\bf (Left)} Mock data distribution on coarse grid for Sdom/DMcuspy. {\bf (Right)} Recover ensemble average kappa distribution.
XXX: Mention log scale and 0== critical density.}
\label{2d mass reconstruction}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp_beta.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp_beta.pdf}
\caption{Estimated projected radially averaged velocity dispersion $\sigma_p$ for two Sdom/DMcuspy models ZConstastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $B=0$ (green) and $B=0$ (blue). In both plots, the actual projected
  velocity dispersion of the mock data (black).
  }
\label{fig:sigp}
\end{figure*}
